\begin{rubric}{Research Experience}
    \entry*[2024 -- ]%
        %
        \textbf{Researcher, Argument Graph Supported Writing Assistance}, \textit{Quantitative}.
        \par Brought on to this 2-year, \$849,799 NSF grant to conduct research on LLM-driven, argument graph construction based on parsed dialectical moves within student essays. Later, I will assist in running and assessing the results of several randomized controlled trials implementing these tools.
        \par\emph{University of Michigan}
        %
    % \entry*[2022 -- 2023]%
    %     %
    %     \textbf{Associate Researcher, English Department Writing Program}, \textit{Mixed Methods}.
    %     \par Invited to conduct research measuring effectiveness and appeal of writing program assignments, using neural topic modeling techniques (LDA2Vec, BERTopic) to provide policy recommendations from 5 years of text-based data spread across 6 different surveys.
    %     \par\emph{University of Michigan}
        %
    \entry*[2019 -- 2023]%
        \textbf{Sweetland Center for Writing Research Associate}, \textit{Quantitative}.
        \par Hired to conduct quasi-experimental research (RDD, panel analysis) on longitudinal data estimating the impact of current placement techniques. Research led to policy changes that erase structures that resulted in poor outcomes for low-income, female, and minoritized students.
        \par\emph{University of Michigan}
        %
    \entry*[2022 -- 2023]%
        \textbf{1619 Project Research Associate}, \textit{Quantitative}.
        \par Scraped a custom, comprehensive database of media covering the 1619 project (Selenium, BeautifulSoup, SQLite). Perform NLP work on the corpus. Manage systemic function linguistic research for a group of 8 manual annotators.
        \par\emph{University of Michigan}
        %
    \entry*[2019 -- 2023]%
        \textbf{College and Beyond II Research Associate}, \textit{Mixed Methods}.
        \par Oversee data storage, cleaning, and utility for a rotating cast of 9 manual annotators within data-secure environment. Research led to 3 journal articles, many conference presentations and webinars.
        \par\emph{Mellon Foundation}
        %
    \entry*[2019]%
        \textbf{Developing Writers in Higher Education Research Assistant}, \textit{Quantitative}.
        \par Brought on to build pipeline for data discovery, scraping, cleaning, annotation, and implementation from scratch using Python, JavaScript to systematically compile the name, email, and affiliation of every Rhet/Comp faculty in the United States.
        \par\emph{University of Michigan}
        %
\end{rubric}