\begin{rubric}{Recognition}
\subrubric{Awards}
\entry*[2022] \textbf{Rackham One-Term Fellow}, Rackham Graduate school.
\entry*[2021] \textbf{Open Education Research Fellow}, Open Education Group.
\entry*[2018] \textbf{American Library Association Innovation in Instruction Award}, ALA.
\entry*[2018] \textbf{3-Minute Thesis Competition — 2nd place}, Brigham Young University.
\entry*[2017] \textbf{Thayer Research Award}. Brigham Young University.
\entry*[2015] \textbf{Larry Thompson Award}, Brigham Young University.
\entry*[2015] \textbf{Pre-Professional Conference: World Literature — 2nd place}, Brigham Young University.
\entry*[2015] \textbf{Pre-Professional Conference: Fiction — 2nd place}, Brigham Young University.
\entry*[2014] \textbf{Research and Creative Works Conference — 2nd place}, Brigham Young University.

\subrubric{Scholarships and Grants}
\entry*[2023] \textbf{Regents' Fellowship}. University of Michigan.
\entry*[2022] \textbf{English Department Travel Grant}. University of Michigan.
\entry*[2020] \textbf{Rackham Conference Travel Grant}. University of Michigan.
\entry*[2019] \textbf{Student Mentoring Block Grant}. Brigham Young University.
\entry*[2018] \textbf{Public Services Travel Committee Award}. Harold B. Lee Library.
\entry*[2017] \textbf{Graduate Travel Award}. Brigham Young University.
\entry*[2017] \textbf{Travel Award}. Society for Comparative Literature and Arts.
\entry*[2017] \textbf{Half-tuition, merit-based scholarship}. Brigham Young University.
\entry*[2015] \textbf{Half-tuition, merit-based scholarship}. Brigham Young University.

\end{rubric}